Beliefs about the development of mental life

### 2021-08-01 paper/paper.Rmd
integrate berent refs

Why do people believe certain aspects of mental life, but not others, to be present at birth? What do people perceive to be driving the development of capacities for _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_? As a first step in what we hope to be a longer line of work addressing such questions, we asked participants to assess the importance of a variety of possible developmental mechanisms for each of the capacities included in this study. We theorized that when people perceive that a capacity is substantially present at birth, they believe that the capacity is innate, and, conversely, that when peopl perceive that a capacity develops slowly over years, they believe the capacity is in some sense learned. (See [@wang.feigenson2019] for an in-depth investigation of ordinary people’s intuitions about the influences of nature vs. nurture in cognitive development, in particular.)

>>>>

Why do people believe certain aspects of mental life, but not others, to be present at birth? What do people perceive to be driving the development of capacities for _bodily sensations_, _negative affect_, _social connection_, and _cognition and control_? As a first step in what we hope to be a longer line of work addressing such questions, we asked participants to assess the importance of a variety of possible developmental mechanisms for each of the capacities included in this study. We theorized that when people perceive that a capacity is substantially present at birth, they believe that the capacity is innate, and, conversely, that when people perceive that a capacity develops slowly over years, they believe the capacity is in some sense learned. (See [@wang.feigenson2019; @berent.etal2019; @berent.etal2020] for in-depth investigations of ordinary people’s intuitions about the innateness of cognitive abilities, motor abilities, and emotion.)
